---
title: "Linear Model"
author: "Yanely Medrano"
date: "7/18/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tigerstats)
library(tidyverse)
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)  
```


## Including Plots

You can also embed plots, for example:



Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.


###Plot scatterplot

```{r}
plot(SIMS~ARM,data=data)
```


##Now with ggplot - first select the basic data

```{r}
basicNN <- ggplot(data,aes(y=SIMS,x=ARM))
```
##Now add in scatterplot

```{r}
basicNN + geom_point()
```
  

The y axis is SIMS and the x axis is ARM. This plot shows that there is a positive linear correlation.

# Numerical results

```{r}
cor(SIMS~ARM,data=data)
```
The value is 0.68, which means that the line will travel upwards and towards the right.   

# Inferential  (Build linear model)
  
```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
```
The evaluation for the line that fits this data is SIMS is equal to -4.1 + .05 * ARM  
The formula needed is y = mx + b to create a line  

  
```{r}
basicNN + geom_point() + geom_smooth(method=lm)
``` 
  
It looks like the value of the y intercept should be around 1.  

